\huge A Better (One-Line!) Title Here

### 2016-10-20 pets2017-paper/pets2017-paper.tex
create a methodology section.

\section{Experimental Setup}
We simulated three environments (which we refer to as E1, E2, and E3), 
which are in the order of increasing severity in censorship. We chose to 
simulate environments for the stability, reproducibility, and simplicity of the 
experiment, as real censored networks are voilatile, subject to change, and complex.

@@

\section{Evaluation Method and Criteria}
\label{sec:eval}

Explain reason for choosing success and time, citing sources. Explain that we made up active configuration time to measure time to completion more accurately since bootstrapping takes so long.

}

\section{Formative Usability Testing}
\label{sec:qualitative}
{\color {blue}
Most usability testing involves finding and fixing problems as part of an iterative design process to make an interface more usable. It is typically called a Formative Usability Evaluation. In contrast, a Summative Usability Evaluation describes the current usability of an interface—as measured by things like task times, completion rates and satisfaction scores. Summative tells you how usable an interface is and formative tells you what isn't usable.

Formative usability testing takes the role of a support tool for decision making during the beginning stages of the design process and - if applied early in the development process - provides valuable insights of where users have difficulty reaching their user goals with the technology (website, desktop GUI design, hardware product) or service.

With formative user testing, it is enough to test 3–5 users. After the fifth user tests, you have all the insight you are likely to get and your best bet is to go back to the drawing board and improve the design so that you can test it again. Testing more than five users wastes resources, reducing the number of design iterations and compromising the final design quality.
%https://www.nngroup.com/articles/usability-metrics/
%https://www.nngroup.com/articles/why-you-only-need-to-test-with-5-users/
}

{\color {red}
\subsection{Recruitment}
Using established practices from the field of user experience research~\cite{howmanyusers},
we recruited 16 participants across the three censorship environments:
5~in E1, 5~in E2, and 6~in E3.
We pre-screened~\cite{screening} our participants for diversity of gender, age, technical expertise,
and self-reported familiarity with Tor in each simulated censorship environment for our summative
usability test~\cite{summative}.

@@

{\color {blue} 
Most usability testing involves finding and fixing problems as part of an iterative design process to make an interface more usable. It is typically called a Formative Usability Evaluation. In contrast, a Summative Usability Evaluation describes the current usability of an interface—as measured by things like task times, completion rates and satisfaction scores. Summative tells you how usable an interface is and formative tells you what isn't usable.

Summative usability testing is a Quality Assurance (QA) type of test usually performed later in the development process. A similar usability test protocol is used as in formative usability testing but now this setup is used to do formal user acceptance testing before the product is released to the target audience. This works on the assumption that the design direction is the right one and that there is potential for a usable solution, and thus the summative usability testing determines whether the execution actually delivers on that promise.

https://www.nngroup.com/articles/usability-metrics/
https://www.nngroup.com/articles/quantitative-studies-how-many-users/
}

>>>>

\section{Methodology}

\subsection{Testing Procedure} 
{\color {blue}

Procedure: inspection, formative, design, summative.

We wanted to inspect the thing ourselves before doing formative testing so we know what to look for. 
http://www.usabilitybok.org/heuristic-walkthrough, not a pluralistic walkthrough (http://www.usabilitybok.org/pluralistic-walkthrough) or cognitive walkthrough (http://www.usabilitybok.org/cognitive-walkthrough).

Most usability testing involves finding and fixing problems as part of an iterative design process to make an interface more usable. It is typically called a Formative Usability Evaluation. In contrast, a Summative Usability Evaluation describes the current usability of an interface—as measured by things like task times, completion rates and satisfaction scores. Summative tells you how usable an interface is and formative tells you what isn't usable.

Formative usability testing takes the role of a support tool for decision making during the beginning stages of the design process and - if applied early in the development process - provides valuable insights of where users have difficulty reaching their user goals with the technology (website, desktop GUI design, hardware product) or service.
%http://www.usabilitybok.org/Formative-evaluation
%https://www.nngroup.com/articles/why-you-only-need-to-test-with-5-users/

With formative user testing, it is enough to test 3–5 users. After the fifth user tests, you have all the insight you are likely to get and your best bet is to go back to the drawing board and improve the design so that you can test it again. Testing more than five users wastes resources, reducing the number of design iterations and compromising the final design quality.

We wanted to try an anternative interface to see if we can make any improvements. We wanted to, since we had all this testing! But we can also test the original design in a formative and summative way.

Summative usability testing is a Quality Assurance (QA) type of test usually performed later in the development process. A similar usability test protocol is used as in formative usability testing but now this setup is used to do formal user acceptance testing before the product is released to the target audience. This works on the assumption that the design direction is the right one and that there is potential for a usable solution, and thus the summative usability testing determines whether the execution actually delivers on that promise.
%http://www.usabilitybok.org/Summative-evaluation
%https://www.nngroup.com/articles/quantitative-studies-how-many-users/
}

\subsection{Evaluation Criteria}
\label{sec:eval}

Explain reason for choosing success and time, citing sources. Explain that we made up active configuration time to measure time to completion more accurately since bootstrapping takes so long. 
}

\subsection{Experimental Setup}
We simulated three environments (which we refer to as E1, E2, and E3), 
which are in the order of increasing severity in censorship. We chose to 
simulate environments for the stability, reproducibility, and simplicity of the 
experiment, as real censored networks are voilatile, subject to change, and complex.

@@

\section{Formative Usability Testing}
\label{sec:qualitative}

{\color {blue}
short intro sentence
}

\subsection{Recruitment}
{\color {red}
Using established practices from the field of user experience research~\cite{howmanyusers},
we recruited 16 participants across the three censorship environments:
5~in E1, 5~in E2, and 6~in E3.
We pre-screened~\cite{screening} our participants for diversity of gender, age, technical expertise,
and self-reported familiarity with Tor in each simulated censorship environment for our summative
usability test~\cite{summative}.

@@

{\color {blue} 
short intro sentence.
}
